# Teaching Lab Demo

This tab demonstrates how to integrate the output of knitted Rmd files into your Shiny app. The server.R pseudo-code is:
```{r server, eval=FALSE}
   # reactiveRmd returns a function that will return the output of knit2html
   # on the Rmd file. Additionally it will only re-run knit2html if the Rmd file
   # has changed.
   teachingRmd <- reactiveRmd('teaching.Rmd',input)

   output$teaching <- reactive(function(){
      # Only call our reactive Rmd function when our tab is visible
      if (input$visibleTab=='Teaching')
         teachingRmd() # returns the HTML
      else
         NULL
   })
```

We can also produce plots:

```{r graphics}
par(mar = c(4, 4, .1, .1))
with(mtcars, {
  plot(mpg~hp, pch=20, col='darkgray')
  lines(lowess(hp, mpg))
})
```

## Inline code

Inline R code is also supported, e.g. the value of `x` is `r x`, and 2 &times; &pi;
= `r 2*pi`.

## Math

LaTeX math as usual: $f(\alpha, \beta) \propto x^{\alpha-1}(1-x)^{\beta-1}$.

## Misc

You can indent code chunks so they can nest within other environments such as lists.

1. the area of a circle with radius x
    ```{r foo}
    pi * x^2
    ```
2. OK, that is great

To compile me, use

```{r compile, eval=FALSE}
library(knitr)
knit('knitr-minimal.Rmd')
```

## Conclusion

Markdown is super easy to write. Go to **knitr** [homepage](http://yihui.name/knitr) for details.
